Project-I by Group MexicoCity

### 2014-11-03 report/paper.tex
report final

We then found that, since Pearson correlation predicted better correlation of square roots than squares but squares were actually better able to decrease test error, it might be a good idea to include 3rd degree transforms of the 11th and 24th variables for logistic regression. After having added them, the test error increased to 0.26656. Thus taking higher orders doesn’t seem to help. We then tried to include a dummy variable transform, but that increased the test error significantly to 0.32625, therefore we’re not going to use them.
\subsection{Penalized logistic regression}
We could improve the test error by cross-validation. The Figure \ref{fig:crossval} shows the three different tests error RMSE, 0-1 loss and log loss. We used different numbers of seeds to have a better prediction for our test error.
\begin{figure}
\centering
\subfigure[0-1 loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegCrossVall01Loss.jpg}}
\subfigure[rmse]{\includegraphics[width=0.6\textwidth]{images/penLogRegrmse.jpg}}
\subfigure[log loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegLogloss.jpg}}
\caption{Cross-validation : penalized logistic regression with different lambda values}
\label{fig:crossval}
\end{figure} 
\section{Summary}
As we have seen, the cross validation helps to have a better test error.\\
We obtained these RMSE for regression.
\begin{description}
\item[leastSquaresGD] We achieved a RMSE of 0.6852
\item[leastSquares] We achieved a RMSE of 0.3317
\item[RidgeRegression] We achieved a RMSE of 0.3073
\end{description}
For the regression, we saw that the best method was Ridge Regression. The best parameter was $\lambda =  39.0694$ and we achieved a test error of 0.3073.

For the classification, the best method was penalized logistic regression. We obtained different results depending the type of error we computed. \begin{description}
\item[RMSE] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.25149.
\end{description}
With logistic regression we obtained different results depending the type of error we computed. \begin{description}
\item[rmse] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.2637.
\end{description}
We see that there is only a small improvement with the log loss error with penalized logistic regression.
The best error we achieved is through the penalized logistic regression method and using the 0-1 loss error.

>>>>

We then found that, since Pearson correlation predicted better correlation of square roots than squares but squares were actually better able to decrease test error, it might be a good idea to include 3rd degree transforms of the 11th and 24th variables for logistic regression. After having added them, the test error increased to 0.26656. Thus taking higher orders doesn’t seem to help. We then tried to include a dummy variable transform, but that increased the test error significantly to 0.32625, therefore we’re not going to use them.
\subsection{Penalized logistic regression}
We could improve the test error by cross-validation. The Figure \ref{fig:crossval} shows the three different tests error RMSE, 0-1 loss and log loss. We used different numbers of seeds to have a better prediction for our test error. For RMSE and 0-1 loss, we tried to change the range of the $\lambda$ parameter but we got the same curve.
\begin{figure}
\centering
\subfigure[0-1 loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegCrossVall01Loss.jpg}}
\subfigure[rmse]{\includegraphics[width=0.6\textwidth]{images/penLogRegrmse.jpg}}
\subfigure[log loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegLogloss.jpg}}
\caption{Cross-validation : penalized logistic regression with different lambda values}
\label{fig:crossval}
\end{figure} 
\section{Summary}
As we have seen, the cross validation helps to have a better test error.\\
We obtained these RMSE for regression.
\begin{description}
\item[leastSquaresGD] We achieved a RMSE of 0.6852
\item[leastSquares] We achieved a RMSE of 0.3317
\item[RidgeRegression] We achieved a RMSE of 0.3073
\end{description}
For the regression, we saw that the best method was Ridge Regression. The best parameter was $\lambda =  39.0694$ and we achieved a test error of 0.3073. This is obtained by removing the categorical, removing the un-correlated variables and using the cube of the 18th and the degree 6 with the 34th variable.

For the classification, the best method was penalized logistic regression. We obtained different results depending the type of error we computed. \begin{description}
\item[RMSE] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.25149.
\end{description}
This is obtained by using the squares and the square root of the 11th and 24th variables.
With logistic regression we obtained different results depending the type of error we computed. \begin{description}
\item[rmse] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.2637.
\end{description}
We see that there is only a small improvement with the log loss error with penalized logistic regression.
The best error we achieved is through the penalized logistic regression method and using the 0-1 loss error.
